Model LF

### 2022-11-06 max_dp endogen stød.Rmd
Commit

@@

plot(((pconk_ds_disc_01 - pconk_ds_disc) / pconk_ds_disc_01), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_disc_01 - ik_disc) / ik_disc), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

>>>>

plot(((yk_ds_02 - yk_ds_bs2)), col= "black", xlab= "Year", ylab= "% Change in BNP", main= "BNP");
grid()
```

@@

plot(((pconk_ds_disc_01 - pconk_ds_disc)), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_disc_01 - ik_disc)), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```
